Key Provisioning for the Internet of Things via Light

### 2015-09-18 paper/paper.tex
small changes in related work

\cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.

In order to secure radio communication, \cite{kuo2007message} utilizes a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
Additionally, another device outside of the cave jams radio waves to prevent malicious communication.

>>>>

\cite{chen2011over} proposes key provisioning using eliptic curve cryptography (ECC).
However, while meeting high security standards, software implementations of ECC require a lot of memory and energy while hardware implementations increase the per-unit cost.
The problem of provisioning (public) keys still remains, too.

In order to secure radio communication, \cite{kuo2007message} utilized a Faraday cage in which a batch of motes can be programmed without interleaving of messages from an attacker outside of the cage.
Additionally, another device outside of the cave jams radio waves to prevent malicious communication.
